Establishing Trusted I/O Paths for Client \\ Shielded Execution Systems with Aurora

### 2019-07-03 sections/main.tex
typo fixes

The SMI handler is initialized by UEFI, and  SMRAM can be locked by configuring D\_OPEN and D\_LCK bits in SMRAM control register. Therefore, the SMI handler is safe from corruption after booting. Moreover, the SMI handler can access all CPU registers, I/O devices, and physical memory (except for SGX EPCs), and thus we expand the SMI Handler to design \textsc{Aurora}'s SMM Supervisor in \autoref{arch}.

@@

%% SMM call，代理+模拟 模式。Enclave的请求最终在SSV处得到响应，和syscall、vmcall是一个道理。
Establishing a trusted path in \textsc{Aurora} consists of the following three steps. First, \textsc{Aurora} builds a secure session between SMM Supervisor (SMVisor) and an enclave that performs an I/O request. Second, SMVisor receives the request via the secure session without leaking knowledge to the untrusted system. Third, SMVisor interacts with the target device on behalf of the enclave, and performs the desired I/O operations to respond to the request. The procedure is conceptually similar to a \textit{syscall} or \textit{vmcall}. We name it an \textit{smcall} for convenience.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.3\textwidth]{figures/mutual.pdf}%height=0.2\textheight,
\caption{Mutual attestation and key agreement between SMM Supervisor and an application enclave. The single line arrows denote the attestation direction, the double line arrow denotes the following key agreement.}
\label{fig:mutual}
\end{figure}

@@

For the case where the hardware clocks are modified in a consistent way, that is, all the timers are altered in the same offset, we propose a novel algorithm to detect such an attack. We use a dedicated counting thread \cite{DBLP:conf/dimva/SchwarzWGMM17} guarded inside an enclave occupying a logical thread on the same CPU core. Such a sibling thread will block the possibility of side-channel attacks when hyper-threading is active. The counting thread provides $dT$ and the difference of hardware timers provides $dt$, we use first-order derivative $dt/dT$ to detect the possible time attack. Currently, we set the confidence interval to 0.05, which denotes the possible altering in the timers' rising slope. If the slope changes much, we assume an attack.

@@

Aurora-OpenSSH client first requests SMVisor to intercept the user's  keyboard events. This interception adds around 13\% overhead per keystroke. Only after SMVisor routes the keyboard interrupt into itself and acknowledges to the client, will the prompt "username@hostname password:"  be displayed on the screen. While the user is typing the passphrase, the client does not display any content on the screen, achieving the same effect as in the native OpenSSH client.

The user's input is buffered inside SMRAM. When the user releases "Enter" key, the password is then encrypted and sent to the secure channel, and SMVisor exits trust input mode.  Aurora-OpenSSH client reclaims the password message and sends it to the server. Note that the plaintext password is only available in SMRAM and enclave. The path between SMRAM and enclave is protected by \textsc{Aurora}'s secure channel and the path between Aurora-OpenSSH client and OpenSSH server is protected by TLS session.
%
%%Recall that SMVisor will manipulate the LED to blink random times to indicate that it has intervened the keyboard interrupts. Because we use virtualized environment to do the experiments, our current prototype uses serial output to indicate this.

@@

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.35\textwidth]{figures/ssl.pdf} %height=0.2\textheight,
%	\caption{Aurora-OpenSSL with trusted clock.}
%	\label{figure:openssl}
%\end{figure}
%There are multiple in-enclave SSL/TLS project on going \cite{mbedtls, intel_sgx_ssl, wolfSSL}. These projects employ SGX to provide tamper-resistant cryptographic process.
SSL/TLS protocols are in widespread use in applications such as web browsing, email, instant messaging, and voice-over-IP. 
%To allow for a distributed communication, a secure session named TLS is established between two parties. 
An SSL/TLS session starts with SSL/TLS handshake protocol, including authentication, key exchange, etc. The procedures rely on system date and time. The SSL/TLS server needs to provide a certificate with a timestamp indicating the expiration time, and the SSL/TLS client needs to verify this certificate. Most of all, both parties require a reliable time source to detect possible timeout. For instance, both "ClientHello" and "ServerHello" messages use the system time to compose \textit{random} field, which is used to prevent replay attacks. If the time is emulated by an untrusted source, it may increase the collision probability of \emph{random} and compromise the security of SSL/TLS.

@@

We evaluated the enhanced SQLite performance by running standardized TPC-H benchmark\footnote{http://www.tpc.org/tpch/} over a large database. % (around 1.3GB).
We modified the benchmark queries in order to make them possible to be executed in SQLite. Unfortunately, not all queries can be executed.
To directly measure the overhead introduced by \textsc{Aurora}'s infrastructure, we set the synchronize flag to \textsf{FULL} to avoid the uncertainty of I/O caching. When SQLite invokes Tlibaurora file APIs, it opens the USB storage device in direct I/O mode and reads/writes data using 4KB block size.
%In our experiment, the native insertion transactions for 1000 times cost 17.3 seconds while the ones with \textsc{Aurora}'s trusted path cost 20.5 seconds. About 18\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.

>>>>

The SMI handler is initialized by UEFI, and  SMRAM can be locked by configuring D\_OPEN and D\_LCK bits in SMRAM control register. Therefore, the SMI handler is safe from corruption after booting. Moreover, the SMI handler can access all CPU registers, I/O devices, and physical memory (except for SGX EPCs), and thus we expand the SMI Handler to design \textsc{Aurora}'s SMVisor in \autoref{arch}.

@@

%% SMM call，代理+模拟 模式。Enclave的请求最终在SSV处得到响应，和syscall、vmcall是一个道理。
Establishing a trusted path in \textsc{Aurora} consists of the following three steps. First, \textsc{Aurora} builds a secure session between SMVisor and an enclave that performs an I/O request. Second, SMVisor receives the request via the secure session without leaking knowledge to the untrusted system. Third, SMVisor interacts with the target device on behalf of the enclave, and performs the desired I/O operations to respond to the request. The procedure is conceptually similar to a \textit{syscall} or \textit{vmcall}. We name it an \textit{smcall} for convenience.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.3\textwidth]{figures/mutual.pdf}%height=0.2\textheight,
\caption{Mutual attestation and key agreement between SMVisor and an application enclave. The single line arrows denote the attestation direction, the double line arrow denotes the following key agreement.}
\label{fig:mutual}
\end{figure}

@@

For the case where the hardware clocks are altered in a consistent way, that is, all the timers are altered in the same offset, we propose a novel algorithm to detect such an attack. We use a dedicated counting thread \cite{DBLP:conf/dimva/SchwarzWGMM17} guarded inside an enclave occupying a logical thread on the same CPU core. Such a sibling thread will block the possibility of side-channel attacks when hyper-threading is active. The counting thread provides $dT$ and the difference of hardware timers provides $dt$, we use first-order derivative $dt/dT$ to detect the possible time attack. Currently, we set the confidence interval to 0.05, which denotes the possible altering in the timers' rising slope. If the slope changes much, we assume an attack.

@@

Aurora-OpenSSH client first requests SMVisor to intercept the user's  keyboard events. This interception adds around 13\% overhead per keystroke. Only after SMVisor routes the keyboard interrupt into itself and acknowledges to the client, will the prompt \textsf{"username@hostname password:"}  be displayed on the screen. While the user is typing the passphrase, the client does not display any content on the screen, achieving the same effect as in the native OpenSSH client.

The user's input is buffered inside SMRAM. When the user releases \textsf{Enter} key, the password is then encrypted and sent to the secure channel, and SMVisor exits trust input mode.  Aurora-OpenSSH client reclaims the password message and sends it to the server. Note that the plaintext password is only available in SMRAM and enclave. The path between SMRAM and enclave is protected by \textsc{Aurora}'s secure channel and the path between Aurora-OpenSSH client and OpenSSH server is protected by TLS session.
%
%%Recall that SMVisor will manipulate the LED to blink random times to indicate that it has intervened the keyboard interrupts. Because we use virtualized environment to do the experiments, our current prototype uses serial output to indicate this.

@@

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.35\textwidth]{figures/ssl.pdf} %height=0.2\textheight,
%	\caption{Aurora-OpenSSL with trusted clock.}
%	\label{figure:openssl}
%\end{figure}
%There are multiple in-enclave SSL/TLS project on going \cite{mbedtls, intel_sgx_ssl, wolfSSL}. These projects employ SGX to provide tamper-resistant cryptographic process.
SSL/TLS protocols are in widespread use in applications such as web browsing, email, instant messaging, and voice-over-IP. 
%To allow for a distributed communication, a secure session named TLS is established between two parties. 
An SSL/TLS session starts with SSL/TLS handshake protocol, including authentication, key exchange, etc. The procedures rely on system date and time. The SSL/TLS server needs to provide a certificate with a timestamp indicating the expiration time, and the SSL/TLS client needs to verify this certificate. Most of all, both parties require a reliable time source to detect possible timeout. For instance, both \emph{ClientHello} and \emph{ServerHello} messages use the system time to compose \textit{random} field, which is used to prevent replay attacks. If the time is emulated by an untrusted source, it may increase the collision probability of \emph{random} and compromise the security of SSL/TLS.

@@

We evaluated the enhanced SQLite performance by running standardized TPC-H benchmark\footnote{http://www.tpc.org/tpch/} over a large database. % (around 1.3GB).
We make minor changes to these benchmark queries in order to make them possible to be executed in SQLite. Unfortunately, not all queries can be executed.
To directly measure the overhead introduced by \textsc{Aurora}'s infrastructure, we set the synchronize flag to \textsf{FULL} to avoid the uncertainty of I/O caching. When SQLite invokes Tlibaurora file APIs, it opens the USB storage device in direct I/O mode and reads/writes data using 4KB block size.
%In our experiment, the native insertion transactions for 1000 times cost 17.3 seconds while the ones with \textsc{Aurora}'s trusted path cost 20.5 seconds. About 18\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.
